Long- and short-read metabarcoding technologies reveal similar spatio-temporal structures in fungal communities

### 2021-03-09 writing/transect_paper.Rmd
rearrange figures so they appear in text ordering
reference S1, 2, 3 in main text

Sampling was conducted at two sites, near the villages of Angaradebou (Ang: N 9.75456° E 2.14064°) and Gando (Gan: N 9.75678° E 2.31058°) approximately 30\ km apart in the _Forêt Classée de l'Ouémé Supérieur_ (Upper Ouémé Forest Reserve) in central Benin.
Both sites were located in West Sudanian savannah woodlands [@olson2001;@yorou2014] dominated by the ECM host tree _Isoberlinia doka_ (Fabaceae tr. Amherstieae).
At each site, 25\ soil samples were collected along a single 24\ m linear transect at intervals of 1\ m in May 2015.
One third of the sample locations (3\ m spacing) were resampled one year later in June 2016, for a total of 67 samples.
For each sample, coarse organic debris was removed from the soil surface and a sample of approximately 5\ cm\ × 5\ cm\ × 5\ cm was extracted with an ethanol sterilized knife blade.
Each sample was sealed in a plastic zipper bag and homogenized by shaking and manually breaking apart soil aggregations.
A subsample of approximately 250\ mg total of soil was collected from two locations in the homogenized soil sample and stored in a DNA preservation buffer before return to the laboratory for extraction (see Supplementary Methods \@ref(Sampling-supplement) for preservation and extraction methods).

>>>>

Sampling was conducted at two sites, near the villages of Angaradebou (Ang: N 9.75456° E 2.14064°) and Gando (Gan: N 9.75678° E 2.31058°) approximately 30\ km apart in the _Forêt Classée de l'Ouémé Supérieur_ (Upper Ouémé Forest Reserve) in central Benin.
Both sites were located in West Sudanian savannah woodlands [@olson2001;@yorou2014] dominated by the ECM host tree _Isoberlinia doka_ (Fabaceae tr. Amherstieae).
At each site, 25\ soil samples were collected along a single 24\ m linear transect at intervals of 1\ m in May 2015.
One third of the sample locations (3\ m spacing) were resampled one year later in June 2016, for a total of 67 samples.
For each sample, coarse organic debris was removed from the soil surface and a sample of approximately 5\ cm\ × 5\ cm\ × 5\ cm was extracted with an ethanol sterilized knife blade.
Each sample was sealed in a plastic zipper bag and homogenized by shaking and manually breaking apart soil aggregations.
A subsample of approximately 250\ mg total of soil was collected from two locations in the homogenized soil sample and stored in a DNA preservation buffer before return to the laboratory for extraction (see Supplementary Methods \@ref(Sampling-supplement), as well as Figures \@ref(buffer-pcoa), \@ref(buffer-compare-long), and \@ref(buffer-compare-short), for preservation and extraction methods).
